---
title: "ODD Data Manipulation & Analysis"
author: "Kerim Acar"
date: "23/11/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
```

# From Raw to Civilized Data

Car sales data downloaded from "Otomotiv Distributorleri Dernegi" website. My part was to obtain January 2016 sales and name of the excel file changed to "odd_retail_sales_2016_01.xlsx".

## Download Raw Data

My raw excel file is in my [repository](pj18-mkerimacar/odd_retail_sales_2016_01.xlsx).
I downloaded that file and put it in a temporary file. Then I read that excel document into R and removed the temp file.
Last two rows also deleted from the dataset since it consists of total sales info which is unnecessary. Then I showed first 10 rows of the dataset.


```{r, cache=TRUE,warning=FALSE,message=FALSE}
tmp<-tempfile(fileext=".xlsx")
download.file("https://github.com/MEF-BDA503/pj18-mkerimacar/blob/master/odd_retail_sales_2016_01.xlsx?raw=true",destfile=tmp)
raw_data<-readxl::read_excel(tmp,skip=7,col_names=FALSE)
file.remove(tmp)
raw_data <- raw_data %>% slice(-c(49,50))
head(raw_data,10)
```

## Make Data Civilized

In order to make the data standardized and workable I renamed column names and removed NA values from the dataset.

```{r, warning=FALSE,message=FALSE}
colnames(raw_data) <- c("brand_name","auto_dom","auto_imp","auto_total","comm_dom","comm_imp","comm_total","total_dom","total_imp","total_total")
car_data_jan_16 <- raw_data %>% mutate_if(is.numeric,funs(ifelse(is.na(.),0,.))) %>% mutate(year=2016,month=1)
print(car_data_jan_16,width=Inf)
```


# Relative Frequencies

I wanted to see relative frequencies of total sales and I created a column named as total_relfreqs next to total sales (rounded to 3 decimals).

```{r}
car_data_jan_16 %>% 
  filter(auto_total > 0 & comm_total > 0) %>%
  select(brand_name,total_total) %>%
  arrange(desc(total_total)) %>%
  mutate(total_relfreqs = (total_total/sum(total_total))) %>%
  mutate(total_relfreqs = sprintf("%0.3f", total_relfreqs))
```

